Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/introduction.tex
Fixes

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose a very
different algorithm that is based on the obvious idea that two points that are
close enough must have the same label. Here, close enough means that they cannot
be separated from each other by a linear separator with a margin.

>>>>

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
very different algorithm for weakly separable data. The algorithm is based on
the obvious idea that two points that are close enough must have the same label.

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class.
In Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the offline
problem of finding a linear multiclass separator consistent with a set of
strongly and weakly labeled examples is NP-hard. In
Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we show that
any algorithm that uses only strongly-labeled examples and ignores weakly
labeled examples makes at least $\Omega\left( \left(1/(160 \gamma)\right)^{(d-2)/4} \right)$
mistakes.

### 2019-01-22 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

\section{Mistake lower bound for ignorant algorithms}
In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}. 
For simplicity, we assume $(x_t, y_t)\in\mathbb{R}^{d}\times [K]$ in this section. 
As the name suggests, ignorant algorithms ignore the examples on which they make mistakes. 
This assumption seems strong, but as we will explain below, it is actually natural, 
and several recently proposed bandit classification algorithms that achieve the $\sqrt{T}$-regret bound belong to this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017}, OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. 
We will see that under the $\gamma$-weak linearly separability assumption, 
if a bandit classification algorithm wants to achieve a mistake bound better than $\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the feature dimension, it must perform some meaningful update when it makes a mistake.

>>>>

\section{Mistake lower bound for ignorant algorithms}
\label{section:mistake-lower-bound-for-ignorant-algorithms}

In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}.
For simplicity, we assume $(x_t, y_t)\in\mathbb{R}^{d}\times [K]$ in this section.
As the name suggests, ignorant algorithms ignore the examples on which they make mistakes.
This assumption seems strong, but as we will explain below, it is actually natural,
and several recently proposed bandit classification algorithms that achieve the $\sqrt{T}$-regret bound belong to this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017}, OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}.
We will see that under the $\gamma$-weak linearly separability assumption,
if a bandit classification algorithm wants to achieve a mistake bound better than $\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the feature dimension, it must perform some meaningful update when it makes a mistake.
